The Need to Develop a Holistic Infectious Disease Surveillance System

### 2024-10-22 manuscript/manuscript.qmd
Clean up manuscript and supplement tables and figures

```{julia}
#| echo: false
include("optimal-thresholds.jl");
```

@@

```{=typst}
#let optimal_thresholds = csv("thresholds.csv")

#table(
  columns: 10,
  fill: (x, y) => {
    if y == 0 {gray}
    if y == 1 {gray}
  },
  align: center,
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 7, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```

@@

```{julia}
#| echo: false
include("line-plots-script.jl");
```

@@

```{julia}
#| fig-cap: "The difference between proportion of the time series in alert for outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-alert-proportion
alert_proportion_line_plot
```

>>>>

```{julia optimal-threshold-setup}
#| echo: false
include("optimal-thresholds-tables.jl");
```

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds.csv")

#table(
  columns: 9,
  fill: (x, y) => {
    if y == 0 {gray}
    if y == 1 {gray}
  },
  align: center,
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 6, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```

@@

```{julia plotting-setup}
#| echo: false
include(srcdir("makie-plotting-setup.jl"));
using OutbreakDetection: line_plot
```

@@

```{julia}
#| fig-cap: "The difference between proportion of the time series in alert for outbreak detection systems under different testing rates and noise structures. The shaded bands illustrate the 80% central interval, and the solid/dashed lines represent the mean estimate."
#| label: fig-alert-proportion
line_plot(
    optimal_threshold_characteristics;
    outcome = :proportion_timeseries_in_alert,
    ylabel = "Proportion of Time Series\nIn Alert",
    hlines = (0.0),
    facet_fontsize = 18,
    labelsize = 20,
    show_x_facet_label = true,
    show_y_facet_label = false,
    ylims = (0, 0.35),
    force = true,
    save_plot = false,
    clinical_hline = clinical_hline,
)
```

### 2024-10-22 manuscript/supplemental-appendix.qmd
Clean up manuscript and supplement tables and figures

#table(
  columns: 10,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 7, align: center, "Testing Rate"),
  ..accuracy.flatten()
)
```

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds-unavoidable.csv")

#table(
  columns: 10,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 7, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds-delays.csv")

#table(
  columns: 10,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 7, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```

>>>>

#table(
  columns: 9,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 6, align: center, "Testing Rate"),
  ..accuracy.flatten()
)
```

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds_unavoidable-cases.csv")

#table(
  columns: 9,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 6, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```

@@

```{=typst}
#let optimal_thresholds = csv("optimal-thresholds_detection-delays.csv")

#table(
  columns: 9,
    fill: (x, y) => {
      if y == 0 {gray}
      if y == 1 {gray}
    },
  [], table.cell(colspan: 2, align: center, "Test Characteristic"), table.cell(colspan: 6, align: center, "Testing Rate"),
  ..optimal_thresholds.flatten()
)
```
